---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
set.seed(11)
```

# huatR

`huatR` (**H**appy **U**sing **a**nd **T**inkering with `R`)[^1] contains `R` functions that I use in my projects. I have finally appreciated the advantages of creating a package to manage one's R functions. `huatR` functions are specifically written for the specific needs of the author (hence the self-serving `yh` prefix) and are probably **not** of interest to most (99.9999%) people. 


[^1]: huatR <https://en.wiktionary.org/wiki/Citations:huat_ah>


## Installation
That said, if you still wish to use it (`NO PANTANG` but *caveat emptor*!), you can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("yhpua/huatR")
```

## Example

```{r example}
library(huatR)
pmtoc()
```

## Code of Conduct

Please note that the 'huatR' project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.

Good Luck & Huat ah!!

