---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
set.seed(11)
```

# huatR

`huatR` (**H**appy **U**sing **a**nd **T**inkering with `R`)[^1] contains `R` functions that I use in my projects. Please note that `huatR` functions are specifically written for the specific needs of the author (which explains the self-serving `yh` prefix) and are probably **not** of interest to most (88.888888 + 8.88888888 + 0.88888888 + 0.088888888 \approx 98.7% [^2])  people.


[^1]: huatR <https://en.wiktionary.org/wiki/huat_ah>
[^2]: The [fixation with 8](https://en.wikipedia.org/wiki/Chinese_numerology#Eight)

## Installation
That said, if you still wish to use it (`NO PANTANG`[^3] but *caveat emptor*!), you can install the development version from [GitHub](https://github.com/) with:

[^3]: [Pantang](https://en.wiktionary.org/wiki/pantang)

``` r
# install.packages("devtools")
devtools::install_github("yhpua/huatR")
```

## Example

```{r example}
library(huatR)
yhnmsd(data = mtcars, mydv = "qsec", dtpoint = "am", tgroup = "vs")
```

## Code of Conduct

Please note that the 'huatR' project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.

Good Luck & Huat ah!!

